Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-21 WSSSPE1_report/WSSSPE1_summary_report.tex
Removes sustainability defs from Sec 5.

The workshop submissions grouped under this section provide frameworks
for thinking about, researching and understanding which elements of sustainability
are important and how they relate. Although there is substantial
overlap between the frameworks, they have different emphases and
extents.  Each paper in this group included a definition of sustainability,
with many overlaps.  In essence the papers related the question to
change over time, an idea well captured in the definition used by the
UK's Scientific Software Sustainability Institute: ``software you use
today will be available---and continue to be improved and
supported---in the future,'' as quoted in~\cite{Venters_WSSSPE}. This
idea was also expressed as software that continues to serve its
users~\cite{Pierce_WSSSPE}.  For a more thorough discussion of definitions
of software sustainability see~\S\ref{sec:defining-sustainability}.

>>>>

The workshop submissions grouped under this section provide frameworks
for thinking about, researching and understanding which elements of sustainability
are important and how they relate. Although there is substantial
overlap between the frameworks, they have different emphases and
extents.  Each paper in this group included a definition of sustainability,
with many overlaps between them  (see Table~\ref{tab:defining-sustainability}).
Perhaps unsurprisingly, the issue of how to define sustainability came
to the fore multiple times during the workshop, and it is thus
summarized in depth separately in ~\S\ref{sec:defining-sustainability}.
